Blocking-resistant communication\\through domain fronting

### 2014-07-15 docs/meek.tex
Ack Johanna from ICSI Notary.
Rewrite abstract with more emphasis on fronting.

\begin{abstract}
We describe meek, a blocking-resistant Internet communication system for censorship circumvention.
meek uses HTTP as a mechanism for transporting data, but it is not a steganographic HTTP transport;
rather, it relies on HTTPS to hide the contents of communications from a censor.
Communications are proxied through a web service that may itself be blocked by the censor:
``domain fronting''---in which the domain name used in the (censor-visible)
DNS request and TLS server name extension doesn't match the name in the (censor-invisible)
HTTP host header---enables communication that is apparently with an allowed host
but actually with a forbidden host.

Though HTTPS frustrates blocking by hiding the underlying communication,
differences in TLS implementations give rise to distinguishing features
that may be used to block circumvention traffic.
We describe how we use a web browser as a tool for making HTTPS requests,
so that the TLS signature of circumvention traffic resembles that of ordinary web browsing.
We present other, more subtle traffic characteristics that may enable blocking,
and identify potential countermeasures to such blocking.

We describe our experience implementing meek as a pluggable transport for Tor,
and the results of an initial experimental deployment.
\end{abstract}

@@

We thank Vern Paxson, Nick Weaver, and Doug Tygar for inspiring conversation on this topic.
Special thanks go to the members of the tor-qa and tor-dev mailing lists
who responded to our design ideas, reviewed source code, and tested our prototypes.
% George Kadianakis
% Georg Koppen
% Lunar
% Yawning Angel
% Rod Hynes and Michael Hull of Psiphon.

>>>>

\begin{abstract}
We describe ``domain fronting,'' an application-layer technique
for HTTPS
that hides the remote endpoint of a communication
for the purpose of censorship circumvention.
Fronting enables a communication stream that is apparently with an allowed domain,
but actually with a forbidden domain.
The technique uses different domain names are used in different
parts of an HTTP request.
One domain is used on the ``outside''---in the DNS request and
TLS Server Name Indication---while another domain is used
on the ``inside''---the HTTP Host header, invisible to the
censor under HTTPS encryption.
A variety of difficult-to-block web services, such as content delivery networks
and Google App Engine, ignore the outside of an HTTPS request
and dispatch it internally according to the Host header:
their frontend servers effectively provide a front,
behind which any domain on their network may be accessed
without revealing the destination to the censor.
If a censor is unable to identify which traffic is fronted,
then blocking the traffic means blocking a content delivery network wholesale,
with resulting expensive collateral damage.
Fronting has been used successfully for a few years by a circumvention system called GoAgent;
we provide a systematic examination of its potential and limitations,
and the results of building an implementation.

We have implemented a system called meek,
a pluggable transport for Tor.
meek combines domain fronting with a simple encoding of a bidirectional byte stream
as HTTPS requests and responses.
A censored client using meek makes a series of HTTPS requests
that appear to be destined to an allowed domain,
but which actually arrive at a special web server on a Tor relay.
The web server decodes the requests, feeds their data into the Tor network,
and sends back any downstream data encoded as HTTPS responses.
We describe our experience deploying meek to Tor users.
meek, or systems inspired by it,
has been adopted by other circumvention systems including Lantern and Psiphon.

Hiding the endpoint and obscuring byte patterns are important parts of blocking-resistant communication,
but there are other, more subtle considerations.
We describe what we have done to disguise other traffic ``tells'' in meek,
such as using a web browser to make HTTPS requests
for a believable TLS fingerprint.
We argue that these measures increase the censor's effort
beyond simple one-shot techniques such as IP address blocking, and into
the realm of more expensive, less reliable statistical tests.
\end{abstract}

@@

We thank Vern Paxson, Nick Weaver, and Doug Tygar for inspiring conversation on this topic.
Special thanks go to the members of the tor-qa and tor-dev mailing lists
who responded to our design ideas, reviewed source code, and tested our prototypes.
% George Kadianakis
% Georg Koppen
% Lunar
% Yawning Angel
% Rod Hynes and Michael Hull of Psiphon.
% Johanna Amann for getting the fraction of SNI from ICSI notary:
%   https://trac.torproject.org/projects/tor/ticket/12208#comment:5
